%-------------------------
% Rezume, a latex resume template for developers
% Author : Nanu Panchamurthy
% Based off of: https://github.com/sb2nov/resume
% License : MIT

% Hope this resume template helps you land an awesome job.
%-------------------------


%------------PACKAGES----------------
\documentclass[a4paper,11pt]{article}

\usepackage{verbatim} % reimplements the "verbatim" and "verbatim*" environments

\usepackage{titlesec} % provides an interface to sectioning commands i.e. custom elements

\usepackage{color} % provides both foreground and background color management

\usepackage{enumitem} % provides control over enumerate, itemize and description

\usepackage{fancyhdr} % provides extensive facilities for constructing headers, footers and also controlling their use

\usepackage{tabularx} % defines an environment tabularx, extension of "tabular" with an extra designator x, paragraph like column whose width automatically expands to fill the width of the environment

\usepackage{latexsym} % provides mathematical symbols

\usepackage{marvosym} % provides martin vogel's symbol font which contains various symbols

\usepackage[empty]{fullpage} % sets margins to one inch and removes headers, footers etc..

\usepackage[hidelinks]{hyperref} % removes color and shadow of hyperlinks

\usepackage[normalem]{ulem} % provides "\ul" (uline) command which will break at line breaks

\usepackage[english]{babel} % provides culturally determined typographical rules for wide range of languages
%-----------------------------------------

\input glyphtounicode % converts glyph names to unicode
\pdfgentounicode=1 % ensures pdfs generated are ats readable

%----------FONT OPTIONS-------------------
\usepackage[default]{sourcesanspro} % uses the font source sans pro
\urlstyle{same} % changes url font from default urlfont to font being used by the document
%-----------------------------------------


%----------MARGIN OPTIONS-----------------
\pagestyle{fancy} % set page style to one configured by fancyhdr
\fancyhf{} % clear all header and footer fields

\renewcommand{\headrulewidth}{0in} % sets thickness of linerule under header to zero
\renewcommand{\footrulewidth}{0in} % sets thickness of linerule over footer to zero

\setlength{\tabcolsep}{0in} % sets thickness of column separator in tables to zero
\setlength{\footskip}{4.08003pt} % sets distance between bottom of footer and bottom of last line of text to 4.08003pt

% origin of the document is one inch from the top and from and the left
% oddsidemargin and evensidemargin both refer to the left margin
% right margin is indirectly set using oddsidemargin
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\topmargin}{-0.5in}

\addtolength{\textwidth}{1.0in} % sets width of text area in the page to one inch
\addtolength{\textheight}{1.0in} % sets height of text area in the page to one inch

\raggedbottom{} % makes all pages the height of current page, no extra vertical space added
\raggedright{} % makes all pages the width of current page, no extra horizontal space added
%------------------------------------------


%--------SECTIONING COMMANDS---------
% \titleformat{<command>}
%   [<shape>]{<format>}{<label>}{<sep>}
%     {<before-code>}[<after-code>]

% command is the sectioning command to be redefined
% shape is the style of the font; scshape stands for small caps style
% format is the format to be applied to whole title- label and text; absent here
% label defines the label
% sep is the horizontal separation between label and title body
% before-code is the code to be executed before
% after-code is the code to be executed after

\titleformat{\section}
  {\scshape\large}{}
    {0em}{\color{blue}}[\color{black}\titlerule\vspace{0pt}]
%-------------------------------------


%--------REDEFINITIONS----------------
% redefines the style of the bullet point
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% redefines the underline depth to 2pt
\renewcommand{\ULdepth}{2pt}
%-------------------------------------


%--------CUSTOM COMMANDS--------------
%\vspace{} defines a vertical space of given size, modifying this in custom commands can help stretch or shrink resume to remove or add content

% resumeItem renders a bullet point
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

% commands to start and end itemization of resumeItem, rightmargin set to 0.11in to avoid the overflow of resumetItem beyond whatever resumeItemHeading is being used
\newcommand{\resumeItemListStart}{\begin{itemize}[rightmargin=0.11in]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% resumeSectionType renders a bolded type to be used under a section, used as skill type here, middle element is used to keep ":"s in the same vertical line
\newcommand{\resumeSectionType}[3]{
  \item\begin{tabular*}{0.96\textwidth}[t]{
    p{0.15\linewidth}p{0.02\linewidth}p{0.81\linewidth}
  }
    \textbf{#1} & #2 & #3
  \end{tabular*}\vspace{-2pt}
}

% resumeTrioHeading renders three elements in three columns with second element being italicized and first element bolded, can be used for projects with three elements
\newcommand{\resumeTrioHeading}[3]{
  \item\small{
    \begin{tabular*}{0.96\textwidth}[t]{
      l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}r
    }
      \textbf{#1} & \textit{#2} & #3
    \end{tabular*}
  }
}

% resumeQuadHeading renders four elements in a two columns with the second row being italicized and first element of first row bolded, can be used for experience and projects with four elements
\newcommand{\resumeQuadHeading}[4]{
  \item
  \begin{tabular*}{0.96\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}
}

% resumeQuadHeadingChild renders the second row of resumeQuadHeading, can be used for experience if different roles in the same company need to added
\newcommand{\resumeQuadHeadingChild}[2]{
  \item
  \begin{tabular*}{0.96\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{\small#1} & {\small#2} \\
  \end{tabular*}
}

% commands to start and end itemization of resumeQuadHeading, lefmargin for left indent of 0.15in for resumeItems
\newcommand{\resumeHeadingListStart}{
  \begin{itemize}[leftmargin=0.15in, label={}]
}
\newcommand{\resumeHeadingListEnd}{\end{itemize}}
%-------------------------------------------


%__________________RESUME____________________
% You can rearrange sections in any order you may prefer
\begin{document}

%-----------CONTACT DETAILS------------------
% Make sure all the details are correct, you can add more links in the first row of second column if needed

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge Garfield Lee \vspace{2pt}} & % row = 1, col = 1
  Location: Shanghai, China \\ % row = 1, col = 2
  \href{https://550.moe/}{\uline{550.moe}} $|$ % row = 2, col = 1
  \href{https://www.linkedin.com/in/garfieldlee/}{\uline{LinkedIn}} $|$ % row = 2, col = 1
  \href{https://github.com/Garfield550}{\uline{GitHub}} & % row = 2, col = 1
  Email: \href{mailto:career@550.moe}{\uline{career@550.moe}} \\ % row = 2, col = 2
\end{tabular*}
%--------------------------------------------


%-----------SUMMARY--------------------------
% Keep this short, simple and straigth to point

\section{Web Developer}
\small{
  \textbf{Five years of experience} as a web developer, I'm familiar with \textbf{React, Next.js, and TypeScript}. I also have experience in Web3 and blockchain development, have worked on projects such as an \textbf{NFT marketplace}, an \textbf{NFT minting platform}, and a \textbf{blog platform based on Web3 technology}. Enjoy trying new web technologies and frameworks, actively promoting and using them in team projects.
}
%--------------------------------------------


%--------------SKILLS------------------------
% Add or remove resumeSectionTypes according to your needs

\section{Technical Skills}
  \resumeHeadingListStart{}
    \resumeSectionType{Languages}{:}{TypeScript, HTML, CSS, C\#, Zig}
    \resumeSectionType{Frameworks}{:}{React, Next.js, NestJS, Node.js}
    \resumeSectionType{Libraries}{:}{Zod, wagmi, Tailwind CSS, Prisma}
    \resumeSectionType{Databases}{:}{PostgreSQL, MySQL}
    \resumeSectionType{Dev Tools}{:}{ESLint, Visual Studio Code, Git, GitHub Copilot}
  \resumeHeadingListEnd{}
%--------------------------------------------


%-----------PROJECTS--------------------------
% Use resumeQuadHeading if four elements are feasible (ex: demo video link), else use resumeTrioHeading. Keep the bullet points simple and concise and try to cover wide variety of skills you have used to build these projects

\section{Projects}
\resumeHeadingListStart{}
  \resumeTrioHeading{Meta Network Homepage}{Next.js, TypeScript, Chakra UI, Emotion}{\href{https://github.com/Meta-Network/meta-ico}{\uline{Source Code}}}
  \resumeItemListStart{}
    \resumeItem{Add new components to the page.}
    \resumeItem{Make the page looks more consistent.}
  \resumeItemListEnd{}

  \resumeTrioHeading{Meta CMS Backend}{NestJS, TypeScript, TypeORM, MySQL, Redis}{\href{https://github.com/Meta-Network/meta-cms-backend}{\uline{Source Code}}}
  \resumeItemListStart{}
    \resumeItem{Build the basic blocks of the project.}
    \resumeItem{Connect to MySQL utilizing TypeORM.}
    \resumeItem{Setup OpenAPI (Swagger) for web developer to consume.}
    \resumeItem{Integrate with Grafana Loki using Winston, logging simultaneously to the terminal, file, and Loki.}
    \resumeItem{Create a corresponding monitoring dashboard for the queueing system built with Bull and NATS.}
    \resumeItem{Add AuthN (authentication) to the app, using JWT passed by in-house UCenter, Passport and NestJS guard.}
    \resumeItem{Utilize microservices architecture design to request basic user information, storage service access token and social media handle from UCenter.}
    \resumeItem{Allow user entering information about their site, which will be passed to Meta CMS Worker after verification using class-validator.}
    \resumeItem{Integrate with GitHub and Gitee, requesting access to a new or existing repository for Worker to store CMS data.}
    \resumeItem{Persist CMS article metadata with Arweave, use pRetry to handle transient failures.}
    \resumeItem{Cache requests using cache-manager, avoiding unnecessary database queries.}
    \resumeItem{Perform unit testing for critical logic with Jest.}
    \resumeItem{Containerize the whole app with Docker Compose.}
  \resumeItemListEnd{}

  \resumeTrioHeading{Meta CMS Worker}{Node.js, TypeScript, Hexo, Git, execa}{\href{https://github.com/Meta-Network/meta-cms-worker}{\uline{Source Code}}}
  \resumeItemListStart{}
    \resumeItem{Encapsulate git(1) with execa, since other mainstream git library in Node.js are basically unusable.}
    \resumeItem{Call internal API of Hexo to create, update and delete articles and to generate websites.}
    \resumeItem{Mux custom configuration from the user with the default configuration, generating a new configuration file for Hexo to consume.}
    \resumeItem{Pushing changes to GitHub or Gitee repository, based on information sent from Backend.}
    \resumeItem{Integrate with Grafana Loki using Winston, logging simultaneously to the terminal, file, and Loki, preventing Denial of Service attack.}
    \resumeItem{Perform unit testing for important logic with AVA and Sinon.JS.}
    \resumeItem{Containerize the whole app with Docker.}
  \resumeItemListEnd{}

  \resumeTrioHeading{ANE NFT Marketplace}{React, TypeScript, styled-components, useSWR, Ethers.js, web3-react}{\href{https://github.com/Artnomics-org/art-and-economics}{\uline{Source Code}}}
  \resumeItemListStart{}
    \resumeItem{Recreate the design draft using styled-components.}
    \resumeItem{Create a decentralized marketplace for ANE with Uniswap Protocol V2 SDK, allowing exchange between ANE token and others, creation of new exchange pairs, and liquidity mining.}
    \resumeItem{Utilizing Zora Media Protocol to handle the creation, bidding and asking of NFTs.}
    \resumeItem{Connect to MetaMask and WalletConnect using Ethers.js and web3-react, allowing users to login and to manage their assets.}
    \resumeItem{Fetch NFT metadata, bids and asks using useSWR.}
    \resumeItem{Extract custom React Hooks from the UI components.}
  \resumeItemListEnd{}

  \resumeTrioHeading{W3itch Fronted}{Next.js, TypeScript, Material UI, Emotion, Ethers.js, useWallet}{}
  \resumeItemListStart{}
    \resumeItem{Crafted using Material UI and Emotion.}
    \resumeItem{Different layouts across the site, providing a better user experience.}
    \resumeItem{AuthN using OAuth 2.0.}
    \resumeItem{Connect with useWallet.}
    \resumeItem{Implement user information and settings form using React Hook Form and class-validator.}
    \resumeItem{AuthZ (authorization) with useContext and useReducer.}
    \resumeItem{Load and paginate data from the backend using getServerSideProps and useSWR.}
    \resumeItem{Allow user to filter games by category and/or tags, implemented with React Select and custom Hooks to synchronize the filter state and the URL, allowing users to share the URL with others.}
    \resumeItem{Manage ERC20 tokens with custom Hooks and Ethers.js.}
    \resumeItem{A11y (accessibility) with ARIA (Accessible Rich Internet Applications).}
    \resumeItem{Split existing large components into several components and custom React Hooks, increasing maintainability.}
    \resumeItem{Prevent unnecessary re-renders using useMemo and useCallback.}
    \resumeItem{Perform unit testing for business logic with Jest.}
  \resumeItemListEnd{}

  \resumeTrioHeading{AmbrusStudio Mint page}{Vue.js, TypeScript, Headless UI, Ethers.js, Web3Modal, wagmi}{}
  \resumeItemListStart{}
    \resumeItem{Mirgate the existing Vue CLI project to Vite.}
    \resumeItem{Implement the page using UnoCSS and Headless UI.}
    \resumeItem{Refactor duplicate code in components, decreasing LoC (Lines of Code) in total.}
    \resumeItem{Author a new Vue component using Vue Composition API, based on Web3Modal HTML and wagmi core, for wallet connection in Vue.}
    \resumeItem{Mint NFTs with wagmi core and Ethers.js, calling in-house seller contract on Ethereum.}
    \resumeItem{Perform unit testing for significant logic with Vitest.}
  \resumeItemListEnd{}

  \resumeTrioHeading{AmbrusStudio User Center}{React, TypeScript, Headless UI, Ethers.js, Web3Modal, wagmi, ImmutableX SDK}{}
  \resumeItemListStart{}
    \resumeItem{Built with Vite, UnoCSS, Headless UI, React Hook Form, Web3Modal and wagmi.}
    \resumeItem{Construct engineering system with Turborepo and pnpm workspace, to share UI components and logic between projects.}
    \resumeItem{Encapsule ImmutableX SDK into a React Hook.}
    \resumeItem{Use AbortController to optimize rendering and network requests.}
    \resumeItem{Refactor filter logic in the gallery, increase rendering performance.}
  \resumeItemListEnd{}

  \resumeTrioHeading{AgentSwap Civitai}{Next.js, TypeScript, tRPC, NextAuth.js, Web3Modal, wagmi, SIWE}{\href{https://github.com/agentswap/civitai}{\uline{Source Code}}}
  \resumeItemListStart{}
    \resumeItem{Utilize NextAuth.js and SIWE (Sign-In With Ethereum) to implement login function.}
    \resumeItem{Share SIWE logic between components using custom React Hooks.}
    \resumeItem{Simplify front-end Hosting Worker API calls using tRPC.}
    \resumeItem{Verify API parameters with Zod.}
    \resumeItem{Create webhook to receive events from Hosting Worker, update the database accordingly.}
  \resumeItemListEnd{}

  \resumeTrioHeading{AgentSwap Hosting Worker}{Node.js, TypeScript, H3, Zod, execa, Octokit, Pino}{\href{https://github.com/agentswap/hosting-worker}{\uline{Source Code}}}
  \resumeItemListStart{}
    \resumeItem{Implement necessary APIs using Node.js and H3.}
    \resumeItem{Output logs to file and terminal with Pino, Pino HTTP and Pino Pretty.}
    \resumeItem{Verify environment variables and API parameters with Zod and h3-zod.}
    \resumeItem{Encapsulate git(1), docker(1) and systemctl(1) (for controlling Caddy) with execa, to build and deploy Gradio projects.}
    \resumeItem{Check if the repository exists, using Octokit and Hugging Face JS libraries.}
  \resumeItemListEnd{}

  % \resumeTrioHeading{If And Only If}{Next.js, TypeScript, Headless UI, Tailwind CSS, Zod, ConnectKit, wagmi}{}
  % \resumeItemListStart{}
  %   \resumeItem{A \textbf{CRUD application} exposed using a RESTful API made with Node.js}
  %   \resumeItem{Exposed POST, GET, PATCH and DELETE HTTP methods using \textbf{Express}}
  % \resumeItemListEnd{}

  \resumeTrioHeading{Taro}{React, TypeScript}{\href{https://github.com/NervJS/taro}{\uline{Source Code}}}
  \resumeItemListStart{}
    \resumeItem{Triage issues on GitHub.}
    \resumeItem{Seasonal contributor to the codebase.}
  \resumeItemListEnd{}

  \resumeTrioHeading{Taro UI}{Taro, React, TypeScript}{\href{https://github.com/NervJS/taro-ui}{\uline{Source Code}}}
  \resumeItemListStart{}
    \resumeItem{Triage issues on GitHub.}
    \resumeItem{Seasonal contributor to the codebase.}
  \resumeItemListEnd{}
\resumeHeadingListEnd{}
%--------------------------------------------


%-----------EXPERIENCE-----------------------
% Distill all your talking points to small bullet points which follow the pattern "challenge-action-result" for maximum efficiency. Try to quantify (use numbers) your points whenver possible, highlist words of importance

\section{Experience}
\resumeHeadingListStart{}

  \resumeQuadHeading{Web Developer}{Nov 2020 -- Jun 2023}
  {Qiubi Technology (Shanghai) Co., Ltd.}{Remote -- Shanghai, China}

    \resumeItemListStart{}
      \resumeItem{I added new features for an enhanced Civitai project, to allow users to use Ethereum wallet login. I created a custom \textbf{NextAuth.js Credentials Provider} and used \textbf{SIWE} for signature verification. \textbf{Web3Modal and wagmi} were used on the front-end to connect to the wallet. To implement the hosting of Gradio projects, I developed a back-end service using \textbf{H3}, validated environment variables and API parameters with \textbf{Zod}, and wrapped Git and Docker commands with \textbf{Execa} to package Gradio projects from GitHub or Hugging Face into Docker images, hosted on the server with custom ports and domains so that the front-end can display Gradio projects.}

      \resumeItem{Collaborated with our CTO to build a back-end service for a web3 blog toolkit. Using \textbf{NestJS, TypeORM, MySQL, and TypeScript}, I completed the back-end API for blog information, storage targets, and theme configuration, and integrated \textbf{Arweave} to store user post's metadata. I built a website generator based on \textbf{Hexo} using \textbf{Node.js}, which can automatically generate and deploy Hexo websites according to the presets provided by the back-end. Received 200 new registrations just on the first day.}

      \resumeItem{I assisted a web3 MOBA game company, developing NFT minting websites and user center websites. I used \textbf{Vue.js, Headless UI, UnoCSS (a Tailwind CSS alternative), and TypeScript} to build the minting website. As Vue does not have a good wallet connection framework, I utilized the \textbf{Vue's Composition API} to encapsulate \textbf{Web3Modal HTML and wagmi Core} to achieve similar functionality as Web3Modal React. During my maintenance of this project, the company successfully conducted four rounds of NFT issuance activities. Together with my colleagues, we built the user center website using \textbf{React and TypeScript}. I split UI elements into components for efficient reuse and also helped optimize some \textbf{React Hooks} to improve page performance. To better reuse UI components and share business logic, I used \textbf{monorepo} to reorganize code from multiple projects into independent packages which solved problems such as copy-pasting and logic synchronization.}
    \resumeItemListEnd{}

  \resumeQuadHeading{Web Developer}{Nov 2018 -- Oct 2020}
  {Shanghai Hayi Information Technology Co., Ltd.}{Shanghai, China}

    \resumeItemListStart{}
      \resumeItem{I am responsible for the development of the company's WeChat Mini Program project. I utilize \textbf{Taro} to standardize the development process and to improve code reuse rate. With Taro's comprehensive support for React, I can easily handle the development and maintenance of different mini-program platforms, effectively reducing development costs. In addition, I also promote \textbf{TypeScript and ESLint} to improve code quality and reduce bugs during production. With my assistance, the company's projects have achieved more efficient development and higher quality code implementation.}

      \resumeItem{I am responsible for customizing the October CMS theme for the company, using \textbf{TypeScript and Sass} to write front-end logic and styles, and using \textbf{Webpack and PostCSS} to package scripts and resource files. By removing messy script tags and style tags, I have reduced issues such as functional failures and style conflicts while increasing code maintainability. Additionally, by integrating commonly used October CMS components and styles into an npm package, I have achieved better code sharing which has improved team development efficiency. With my assistance, our clients have received a better user experience with higher quality project implementation.}
    \resumeItemListEnd{}

  \resumeQuadHeadingChild{Software Developer Intern}{Aug 2017 -- Feb 2018}

    \resumeItemListStart{}
      \resumeItem{Assisted lead developer maintaining and developing new features using C\# and ASP.NET Core.}
    \resumeItemListEnd{}

\resumeHeadingListEnd{}
%---------------------------------------------


%-----------EDUCATION-------------------------
% Mention your CGPA, if its good, in the first row of second column

\section{Education}
  \resumeHeadingListStart{}
    \resumeQuadHeading{Shandong Vocational College of Information Technology}{Weifang, Shandong, China}
    {Software Engineering}{Jul 2015 -- Jul 2018}
  \resumeHeadingListEnd{}
%---------------------------------------------


%----------------OTHERS----------------------
% You can add your acheivements, accolades, certifications etc. here.

%\section{Certifications}
%  \resumeItemListStart{}
%    \resumeItem{\href{https://dummy-certification.com}{\uline{Certified Web Developer by the W3C}}}
%    \resumeItem{\href{https://dummy-certification.com}{\uline{Microsoft Certified: Azure Developer Associate}}}
%    \resumeItem{\href{https://dummy-certification.com}{\uline{AWS Certified Developer - Associate}}}
%  \resumeItemListEnd{}
%--------------------------------------------

\end{document}
